\begin{abstract}
In this publication,
I suggest technique to apply systematic and stochastic local search 
for combinatorial optimization problem 
by using Answer Set Programming,
one of the developed form of SAT. %%
The suggestion is based on 
Large Neighborhood Search,
a kind of approximate solution method.
LNS is iterative solution method,
that cancels a part of assignment of variables 
included in the solution at random 
and rebuild solution 
by reassign only the variables. %%
In the suggestion, 
I permit reassignment to the variable 
that was not canceled 
by replacing rebuilding solution 
with re-search that maintained assignment 
if possible. %%
In this way, 
I can perform the search 
that does not depend too much 
which assignment you cancel. %%
I implemented suggestion technique 
on ASP solver clingo 
and evaluate performance 
using benchmarks of the 
International Timetabling Competition (all 21 problems). %%
As a result, 
the suggestion was able to get 
a better solution for many problems 
in comparison with normal ASP. %%
In addition, 
I succeeded in updating the known best value 
at one problem.

%本発表では，SAT の発展形の一つである解集合プログラミング (Answer Set
%Programming; ASP) 技術を用い，組合せ最適化問題に対して系統的探索と確率
%的局所探索を統合的に適用する手法を提案する．

%提案手法は，近似解法の一種である巨大近傍探索 (Large Neighborhood
%Search; LNS) のアイデアをベースにしている．LNS は解に含まれる変数の値
%割当ての一部をランダムに選んで取り消し，その変数のみに対して再割当てを
%行うことで解を再構築する反復解法である．提案手法では，解の再構築の操作
%を，値割当てをなるべく維持したままでの再探索に置き換えることで，取り消
%されなかった変数への再割当てを許す．これによって，どの値割当てを取り消
%すかに依存しすぎない探索を行うことができる．

%提案手法を ASP ソルバー clingo 上に実装し，国際時間割競技会の問題集(全
%21問)を用いて性能評価を行った．その結果，提案手法は，通常の ASP 解法と
%比較して，多くの問題に対してより良い解を得ることができた．また，1問に
%ついて，既知の最良値を更新することに成功した．
\end{abstract}

%\setcounter{page}{1}
\def\Style{``jsaiac.sty''}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em%
 T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\def\JBibTeX{\leavevmode\lower .6ex\hbox{J}\kern-0.15em\BibTeX}
\def\LaTeXe{\LaTeX\kern.15em2$_{\textstyle\varepsilon}$}

\begin{document}
\maketitle